Scalar and Representative Observables for Polarimetric SAR Data

### 2013-09-25 paper_dev/article_pp.tex
for work in isprint

The previous section  introduced  theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
This section will show that the model is equally  applicable to the 1-dimensional ($d=1$) case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
  as well as reminding us that SAR is a special case of POLSAR.

The results for our models can be summarized using the following equations:
\begin{align}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
\end{align}

Upon setting $d=1$ into the above equations,
  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
%Upon setting $d=1$ into the above models,
%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
\begin{align*}
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{eqnarray}
Furthermore, the following derivations for multi-look SAR data
   show that it can be considered 
    either as extensions of the corresponding single-look SAR results
    or as simpler case of the POLSAR results:
  \begin{align*}
    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
  \end{align*}

\section{Validating the proposed models against real-life data}
\label{sec:polsar_models_validation}

This section aims to verify the theoretical models against practical data.
Since it is shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  which have been validated extensively, only a simple validation is presented for this case.

Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
 The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
%The ENL is set to the nominal number of 4.
%And good visual match is apparent in the final results.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[multi-look SAR dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[multi-look SAR contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
		 \label{multi_look_contrast}
	}
\end{tabular}
\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[multi-look SAR log-distance]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[multi-look SAR contrast]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
		 \label{multi_look_contrast}
	}
\end{tabular}
\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
\end{figure}
%endif

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
While the match appears to be reasonably good, it can be further improved.
Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.

%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
%While the match appears to be reasonably good, it can be further improved.
%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.

\subsection{Using the nominal ENL to validate the theoretical models} 
\label{sec:valid_nominal_enl}

The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.

For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
Both the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.

The least-assumed stochastic processes for dispersion and contrast are validated first.
For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.

At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
Here a nominal look-number L=4 is used
  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
The plots, presented in Fig.
  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}
%endif

Apart from dispersion and contrast,
  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
There are two ways to estimate this quantity over an homogeneous area.
The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
Both approaches will be presented in this section.
As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.

Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
  and \ref{eqn:log_determinant_distance_distribution},
  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
A close match is again observed, validating the models for log-distance and determinant ratio.

>>>>

The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
This section will show that the model is equally  applicable to the 1-dimensional ($d=1$) case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
Hence this derivation can be considered
  either as cross-validation for the proposed POLSAR model
  or as evidence showing that
    the generic POLSAR model proposed in this article also covers the traditional model for SAR intensity in its natural coverage.
%  as well as reminding us that SAR is a special case of POLSAR.

The results for our models can be summarized using the following equations:
\begin{align*}
  |C_v| &\sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
%  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
%  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
%  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
%  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
%  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
%  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
\end{align*}

Upon setting $d=1$ into the above equations,
  the becomes:
\begin{align*}
  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
\end{align*}

Since the PDF of chi-squared distribution can be written as:
\begin{align*}
\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
\end{align*}
, applying variable change theorem into the above equations results in:
\begin{align*}
  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
\end{align*}
These equations match exactly with the following traditional model for multi-look SAR intensity:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
  \end{eqnarray}
considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.

\section{Discussion}

\subsection{Validating the proposed models against real-life data}
\label{sec:polsar_models_validation}

This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
Both of these models require the estimation of two parameters from some given captured data.
They are the dimensional number $d$ and the look number $L$.
The dimensional number $d$ is related to the type of (POL)SAR data,
  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
The look-number $L$ can be taken either as nominally stated by the data provider,
  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
To show the robustness of the proposed models, their validation is also put to test on different types of POLSAR sensors.
Specifically in this article, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
  a fine-quad single-look complex RADARSAT2 image ($L=1$) are employed.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  which have been validated extensively, the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
The histograms for both the intensity and intensity ratio (TODO:Replot) %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
The plots are obtained with ENL set to both the nominal number of 4 and the estimated number of (TODO:CALC).
Also presented are the plots of the same experiment applied on a homogeneous patch inside the nine-look processed RADARSAT2 image (TODO:NewPlot).
In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
In all cases, good visual match is apparent, which validates the model proposed above. %providing us a simple validation of the result.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	} \\
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_1D}
\end{figure}
%endif

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Similar experiments like the one described for SAR data is carried out
  for both types of polarimetric SAR
  on both AIRSAR and RADARSAT2 datasets.
The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH-HV) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_2D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
		 \label{RADARSAT2_2D_determinant}
	} \\
	\subfloat[AIRSAR (HH-HV) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_2D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
		 \label{RADARSAT2_2D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH-HV) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_2D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
		 \label{RADARSAT2_2D_det_ratio}
	}
\end{tabular}
\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_2D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[RADARSAT2 (HH-HV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
		 \label{RADARSAT2_2D_determinant}
	}
	\hfill	
	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
 	\hfill	
	\subfloat[RADARSAT2 (HH-HV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
		 \label{RADARSAT2_2D_determinant}
	} \\
	\subfloat[AIRSAR (HH-HV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_2D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH-HV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[AIRSAR (HH-HV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
\end{tabular}
\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_2D}
\end{figure}
%endif

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH-HV-VV) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	} \\
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_2D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_2D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_2D_change_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_2D_change_ratio}
	}
\end{tabular}
\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_3D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH-HV-VV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_change_ratio}
	} \\
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	}
        \hfill
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_1D_change_ratio}
	}
\end{tabular}
\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_3D}
\end{figure}
%endif

\subsection{Theoretical Implications of This Proposal}
\label{sec:discussion}
